Lexical frequency mediates the facilitation effect of cognateness in bilingual lexical acquisition

### 2023-05-01 _appendix/_model-diagnostics.qmd
Add appendix for syllable frequencies and new revisions
Upgrade bvq package and change targets workflow

```{r apafg-model-ppc}
#| label: apafg-model-ppc
#| apa-cap: "Model posterior predictive checks (PPC). Bars indicate the observed proportion of responses to each category (No, Understands, and Understands and Says). Blue dots and error bars represent the mean proportion of responses simulated from the posterior for each category, and its 95\\% interval."
#| eval: true
#| echo: false
#| warning: false
#| message: false
#| fig-width: 6
#| fig-height: 3
#| out-width: 50%
#| out-height: 50%
y_int <- as.integer(as.integer(responses$response))
color_scheme_set(c(rep("grey60", 2), rep("black", 4)))

>>>>

```{r apafg-model-ppc}
#| label: apafg-model-ppc
#| apa-cap: "Model posterior predictive checks (PPC). Bars indicate the observed proportion of responses to each category (No, Understands, and Understands and Says). Blue dots and error bars represent the mean proportion of responses simulated from the posterior for each category, and its 95\\% interval."
#| eval: true
#| echo: false
#| warning: false
#| message: false
#| fig-width: 6
#| fig-height: 3
#| out-width: 80%
#| out-height: 80%
y_int <- as.integer(as.integer(responses$response))
color_scheme_set(c(rep("grey60", 2), rep("black", 4)))
